The hedging hyperprior for the normal distribution: unknown mean, unknown precision

### 2023-03-22 text/23/normal-hedging-hyperprior-part-3.Rmd
Tweaking formulas in normal-hedging-hyperprior-part-3

$g(\mu) = \int
  \sqrt{\frac{\tau}{2 \pi}}
  e^{-\frac{1}{2}\tau (\mu-\mu_0)^2}
  \frac{(n_0 \tau_0)^{n_0}}{\Gamma(n_0)}
  \tau^{n_0-1}
  e^{-\beta_0 \tau}d\tau$

Pull out any multiplicative constants not involve $\tau$.

$g(\mu) = 
  \frac{1}{\sqrt{2 \pi}}
  \frac{(n_0 \tau_0)^{n_0}}{\Gamma(n_0)}
  \int\tau^{n_0-\frac{1}{2}}
  e^{-\tau(\frac{1}{2} (\mu-\mu_0)^2-\beta_0)}
  d\tau$

>>>>

$g(\mu) = \int
  \sqrt{\frac{\tau}{2 \pi}}
  e^{-\frac{1}{2}\tau (\mu-\mu_0)^2}
  \frac{(n_0 \tau_0)^{n_0}}{\Gamma(n_0)}
  \tau^{n_0-1}
  e^{-\frac{n_0 \tau}{\tau0}}d\tau$

Pull out any multiplicative constants not involving $\tau$.

$g(\mu) = 
  \frac{1}{\sqrt{2 \pi}}
  \frac{(n_0 \tau_0)^{n_0}}{\Gamma(n_0)}$
  \int\tau^{n_0-\frac{1}{2}}
  e^{-\tau(
    \frac{1}{2}(\mu-\mu_0)^2 - 
    \frac{n_0}{\tau0}}d\tau)$

What remains inside the integral could be a gamma distribution with

$\alpha=n_0 + \frac{1}{2}$

$\beta = 
  \frac{1}{2}(\mu-\mu_0)^2 - 
  \frac{n_0}{\tau0}$

if there were the correct normalizing constants. Multiply inside the integral by the normalizing constant

$\frac{(\frac{1}{2} (\mu-\mu_0)^2-\frac{n0}{\tau_0})^{n_0 + \frac{1}{2}}}{\Gamma(n_0+ \frac{1}{2})}$

When you divide outside by the normalizing constant, you get

$\frac{1}{\sqrt{2 \pi}}$
$\frac
  {(n_0 \tau_0)^{n_0}}
  {\Gamma(n_0)}$
$\frac
  {\Gamma(n_0 + \frac{1}{2})}
  {(\frac{1}{2} (\mu-\mu_0)^2 - 
     \frac{n0}{\tau_0})^
       {n_0 + \frac{1}{2}}}$

$\frac
    {\Gamma \left(\frac{\nu+1}{2} \right)}
    {\sqrt{\nu\pi}\,\Gamma \left(\frac{\nu}{2} \right)}
  \left(1+\frac{x^2}{\nu} \right)^{-\frac{\nu+1}{2}}$
